---
title: "Non-Linear Regression Models"
author: "Applied Machine Learning Tutorial"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

## Introduction

In multiple linear regression, we assume a *linear relationship* between predictors and response variables. However, in practice, relationships may be **nonlinear**.  
To model such data more accurately, we can **extend linear models** using polynomial terms, splines, and smoothers while keeping the model interpretable and flexible.

---

## 1. Polynomial Regression

Polynomial regression fits a curve by including higher-order terms of $x$.

The model for degree 2 is:

$$
y = \beta_0 + \beta_1 x + \beta_2 x^2 + \epsilon
$$

### Example

```{r}
library(tidyverse)

set.seed(42)
x <- runif(100, 0, 10)
y <- 2 + 0.5 * x - 0.1 * x^2 + rnorm(100, 0, 1)
data <- tibble(x, y)

# Fit a polynomial regression model
fit_poly <- lm(y ~ poly(x, 2, raw = TRUE), data = data)
summary(fit_poly)

# Plot
ggplot(data, aes(x, y)) +
  geom_point() +
  stat_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = FALSE, color = "blue") +
  labs(title = "Polynomial Regression", y = "y", x = "x")
```

---

## 2. Step Functions (Digitization / Categorization)

Step functions divide the range of $x$ into intervals and fit a constant value in each.

### Example

```{r}
# Create cut-points
data <- data %>%
  mutate(x_cut = cut(x, breaks = c(0, 3, 6, 10)))

fit_step <- lm(y ~ x_cut, data = data)
summary(fit_step)

ggplot(data, aes(x, y)) +
  geom_point() +
  geom_vline(xintercept = c(3, 6), linetype = "dashed") +
  labs(title = "Step Function Regression")
```

---

## 3. Basis Functions

A **basis function** transforms predictors before fitting a linear model.
Common bases include polynomial, step, spline, or other nonlinear transformations.

General form:
$$
y = \beta_0 + \beta_1 b_1(x) + \beta_2 b_2(x) + \dots + \beta_K b_K(x) + \epsilon
$$

Example with a simple power basis:

```{r}
basis1 <- x
basis2 <- x^2
basis3 <- x^3

fit_basis <- lm(y ~ basis1 + basis2 + basis3)
summary(fit_basis)
```

---

## 4. Regression Splines

Splines divide the data into regions separated by **knots**, fitting low-degree polynomials that connect smoothly at each knot.

### Example using `splines` package

```{r}
library(splines)

fit_spline <- lm(y ~ bs(x, knots = c(3, 6), degree = 3), data = data)
summary(fit_spline)

ggplot(data, aes(x, y)) +
  geom_point() +
  geom_line(aes(y = predict(fit_spline)), color = "red") +
  labs(title = "Regression Spline")
```

---

## 5. Smoothing Splines

A **smoothing spline** chooses the smoothest function that balances fit and smoothness, controlled by $\lambda$ (the smoothing parameter).

### Example

```{r}
fit_smooth <- smooth.spline(x, y, cv = TRUE)

plot(x, y, main = "Smoothing Spline", xlab = "x", ylab = "y")
lines(fit_smooth, col = "blue", lwd = 2)
```

---

## 6. Local Regression (LOESS)

**Local regression** fits simple models to localized subsets of the data, allowing flexible fitting.

### Example

```{r}
fit_loess <- loess(y ~ x, span = 0.5)

ggplot(data, aes(x, y)) +
  geom_point() +
  geom_smooth(method = "loess", span = 0.5, se = FALSE, color = "darkgreen") +
  labs(title = "Local Regression (LOESS)")
```

---

## 7. Generalized Additive Models (GAM)

**GAMs** extend linear models by fitting smooth functions of each predictor:

$$
y = \beta_0 + f_1(x_1) + f_2(x_2) + \dots + \epsilon
$$

### Example

```{r}
library(mgcv)

# Generate 2D example data
set.seed(123)
x1 <- runif(100, 0, 10)
x2 <- runif(100, 0, 10)
y <- 2 + sin(x1) + 0.5 * x2 + rnorm(100, 0, 0.5)
df <- data.frame(x1, x2, y)

fit_gam <- gam(y ~ s(x1) + s(x2), data = df)
summary(fit_gam)
plot(fit_gam, pages = 1)
```

---

## Summary

| Technique             | Flexibility | Interpretability | R Functions       |
| --------------------- | ----------- | ---------------- | ----------------- |
| Polynomial Regression | Moderate    | High             | `lm()`, `poly()`  |
| Step Function         | Low         | High             | `cut()`, `lm()`   |
| Regression Splines    | High        | Moderate         | `bs()`            |
| Smoothing Splines     | Very High   | Moderate         | `smooth.spline()` |
| Local Regression      | Very High   | Moderate         | `loess()`         |
| GAM                   | Very High   | Moderate         | `gam()`, `s()`    |

---

## References

* James, Witten, Hastie, Tibshirani (2021). *An Introduction to Statistical Learning (2nd Ed.)*. Springer.
* UCI Machine Learning Repository
* R Documentation for `splines`, `mgcv`, and `tidymodels`

