
---
title: "2‑Day Practical Handout: Neural Networks & LLMs (R • Python • Julia)"
author: "Your Name"
date: "2025-08-26"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: show
  pdf:
    documentclass: article
    toc: true
jupyter: true
---

> Four 60‑minute sessions across two days. All examples run on a typical laptop (8–16GB RAM). Choose **R**, **Python**, or **Julia** (or mix).

## Learning goals
- Explain core NN/LLM terminology (neuron, activation, loss, gradient, epoch, batch; token, embedding, attention, transformer).
- Train a small neural network for classification on a toy dataset.
- Build and train a tiny character‑level language model on a short text corpus and sample from it.
- Evaluate models and avoid overfitting with train/validation splits, regularization, and early stopping.

## Prerequisites
Linear algebra (vectors/matrices, dot products), multivariable calculus (gradients), probability basics.

## Setup (pick one or more languages)

### R (lightweight path)
```{r}
install.packages(c("tidyverse","nnet","caret","torch"))
# One-time torch install (downloads backend):
torch::install_torch()
```

### Python (recommended for LLM mini-labs)
```{bash}
python -m venv .venv && source .venv/bin/activate
pip install --upgrade numpy pandas scikit-learn torch
```

### Julia
```{julia}
using Pkg
Pkg.add(["CSV","DataFrames","Flux","MLDataUtils","Random","Statistics"])
```

::: callout-tip
If installs are slow, complete Sessions 1–2 with **R `nnet`** or **Python `scikit-learn`** and skip torch/Flux.
:::

## Schedule

**Day 1**  
- **S1 (60m):** Neural network basics + MLP classifier  
- **S2 (60m):** Training loops, optimization, and evaluation  

**Day 2**  
- **S3 (60m):** LLM concepts + build a tiny character model  
- **S4 (60m):** Sampling, embeddings mini‑lab, and extensions  

---

## Shared mini‑datasets (generated on the fly)

### 1) Two‑class spiral for classification

#### R
```{r}
make_spiral <- function(n=1000, noise=0.2){
  set.seed(42)
  n2 <- n/2
  t <- seq(0,1,length.out=n2)
  r <- t*2.5
  a <- t*4*pi
  x1 <- c(r*cos(a) + rnorm(n2,0,noise), r*cos(a+pi) + rnorm(n2,0,noise))
  x2 <- c(r*sin(a) + rnorm(n2,0,noise), r*sin(a+pi) + rnorm(n2,0,noise))
  y  <- factor(c(rep(0,n2),rep(1,n2)))
  data.frame(x1,x2,y)
}
spiral <- make_spiral()
head(spiral)
```

#### Python
```{python}
import numpy as np
def make_spiral(n=1000, noise=0.2, seed=42):
    rng = np.random.default_rng(seed)
    n2 = n//2
    t = np.linspace(0,1,n2)
    r = t*2.5
    a = t*4*np.pi
    x1 = np.concatenate([r*np.cos(a) + rng.normal(0,noise,n2),
                         r*np.cos(a+np.pi) + rng.normal(0,noise,n2)])
    x2 = np.concatenate([r*np.sin(a) + rng.normal(0,noise,n2),
                         r*np.sin(a+np.pi) + rng.normal(0,noise,n2)])
    y  = np.concatenate([np.zeros(n2,dtype=int), np.ones(n2,dtype=int)])
    X = np.stack([x1,x2],axis=1)
    X, y
```

#### Julia
```{julia}
using Random
function make_spiral(n::Int=1000, noise::Float64=0.2; seed=42)
    Random.seed!(seed)
    n2 = div(n,2)
    t = range(0,1,length=n2)
    r = 2.5 .* collect(t)
    a = 4π .* collect(t)
    x1 = vcat(r .* cos.(a) .+ noise .* randn(n2), r .* cos.(a .+ π) .+ noise .* randn(n2))
    x2 = vcat(r .* sin.(a) .+ noise .* randn(n2), r .* sin.(a .+ π) .+ noise .* randn(n2))
    y  = vcat(zeros(Int,n2), ones(Int,n2))
    hcat(x1,x2), y
end
```

### 2) Tiny text corpus
```{markdown}
In mathematics we write x^2 + y^2 = r^2. Proofs rely on axioms and logic.
Sequences, limits, and derivatives shape analysis. Probability models uncertainty;
linear algebra powers neural networks via matrix multiplication.
```

---

# Day 1 — Session 1: NN basics + MLP classifier

## Key terms
Neuron (affine + nonlinearity), activation (ReLU/tanh/sigmoid), loss (cross‑entropy), gradient, optimizer (SGD/Adam), epoch/batch, overfitting.

## Math core
One layer: \(f(x)=\sigma(Wx+b)\). Softmax for \(k\) classes:  
\[ \hat{y} = \operatorname{softmax}(Wx+b), \quad L = -\sum_{i=1}^k y_i \log(\hat{y}_i). \]  
Gradient descent: \(\theta \leftarrow \theta - \eta\, \nabla_\theta L\).

## Quick win (R, `nnet`)
```{r}
library(tidyverse); library(nnet); library(caret)
set.seed(1)
spiral <- make_spiral(1000,0.2)
idx <- createDataPartition(spiral$y,p=0.8,list=FALSE)
train <- spiral[idx,]; test <- spiral[-idx,]
m <- nnet(y ~ x1 + x2, data=train, size=16, decay=1e-3, maxit=500, trace=FALSE)
pred <- predict(m, newdata=test, type="class")
mean(pred==test$y)
```

## Quick win (Python, scikit‑learn)
```{python}
from sklearn.model_selection import train_test_split
from sklearn.neural_network import MLPClassifier
from sklearn.metrics import accuracy_score
X,y = make_spiral(1000,0.2)
Xtr,Xte,ytr,yte = train_test_split(X,y,test_size=0.2,random_state=1,stratify=y)
clf = MLPClassifier(hidden_layer_sizes=(16,), activation='tanh', alpha=1e-3, max_iter=1000, random_state=0)
clf.fit(Xtr,ytr)
accuracy_score(yte, clf.predict(Xte))
```

## Quick win (Julia, Flux)
```{julia}
using Flux, Random, Statistics
X,y = make_spiral(1000,0.2)
Xf = permutedims(Float32.(X))  # 2 × N
yf = Flux.onehotbatch(y .+ 1, 1:2)
model = Chain(Dense(2,16,tanh), Dense(16,2), softmax)
loss(x, y) = Flux.logitcrossentropy(model(x), y)
opt = Flux.ADAM(1e-2)
for epoch in 1:2000
    Flux.train!(loss, params(model), [(Xf, yf)], opt)
end
ŷ = onecold(model(Xf)) .- 1
mean(ŷ .== y)
```

---

# Day 1 — Session 2: Training loops, optimization, evaluation

## PyTorch training loop (transferable to R torch / Flux)
```{python}
import torch, torch.nn as nn
X_np, y_np = make_spiral(1000,0.2)
X = torch.tensor(X_np, dtype=torch.float32)
y = torch.tensor(y_np, dtype=torch.long)
model = nn.Sequential(nn.Linear(2,16), nn.Tanh(), nn.Linear(16,2))
opt = torch.optim.Adam(model.parameters(), lr=1e-2)
loss_fn = nn.CrossEntropyLoss()
for epoch in range(1000):
    opt.zero_grad()
    logits = model(X)
    loss = loss_fn(logits, y)
    loss.backward()
    opt.step()
float(loss)
```

## Early stopping via validation split (R)
```{r}
set.seed(2)
idx <- createDataPartition(spiral$y,p=0.8,list=FALSE)
train <- spiral[idx,]; valid <- spiral[-idx,]
best <- Inf; best_m <- NULL
for(s in c(8,16,32)){
  m <- nnet(y ~ x1 + x2, data=train, size=s, decay=1e-3, maxit=500, trace=FALSE)
  vpred <- predict(m, newdata=valid, type="class")
  err <- 1-mean(vpred==valid$y)
  if(err<best){ best<-err; best_m<-m }
}
best
```

---

# Day 2 — Session 3: LLM concepts + tiny character model

## Key terms
Token/embedding, self‑attention, positional encoding, pretraining vs fine‑tuning, inference vs training cost.

## Minimal character‑level model (Python, GRU)
```{python}
import torch, torch.nn as nn
text = (
"In mathematics we write x^2 + y^2 = r^2. Proofs rely on axioms and logic.
"
"Sequences, limits, and derivatives shape analysis. Probability models uncertainty;
"
"linear algebra powers neural networks via matrix multiplication."
)
chars = sorted(list(set(text)))
stoi = {ch:i for i,ch in enumerate(chars)}
itos = {i:ch for ch,i in stoi.items()}
X = torch.tensor([stoi[c] for c in text[:-1]], dtype=torch.long)
Y = torch.tensor([stoi[c] for c in text[1:]], dtype=torch.long)
embed = nn.Embedding(len(chars), 16)
rnn = nn.GRU(16, 64, batch_first=True)
head = nn.Linear(64, len(chars))
opt = torch.optim.Adam(list(embed.parameters())+list(rnn.parameters())+list(head.parameters()), lr=2e-2)
loss_fn = nn.CrossEntropyLoss()
for epoch in range(400):
    xemb = embed(X).unsqueeze(0)  # (1,T,16)
    out,_ = rnn(xemb)
    logits = head(out).squeeze(0)
    loss = loss_fn(logits, Y)
    opt.zero_grad(); loss.backward(); opt.step()
float(loss)
# Sampling
with torch.no_grad():
    ch = torch.tensor([stoi['I']])
    h = None; out_chars = []
    for _ in range(300):
        emb = embed(ch).unsqueeze(0)
        o,h = rnn(emb,h)
        logits = head(o.squeeze(0))
        p = torch.softmax(logits[-1],dim=0)
        ch = torch.multinomial(p,1)
        out_chars.append(itos[int(ch)])
    "".join(out_chars)
```

## R (torch) variant
```{r}
library(torch)
text <- "In mathematics we write x^2 + y^2 = r^2. Proofs rely on axioms and logic.
Sequences, limits, and derivatives shape analysis. Probability models uncertainty;
linear algebra powers neural networks via matrix multiplication."
chs <- sort(unique(strsplit(text,"")[[1]]))
stoi <- setNames(seq_along(chs)-1, chs); itos <- setNames(chs, seq_along(chs)-1)
X <- torch_tensor(match(strsplit(substr(text,1,nchar(text)-1),"")[[1]], chs)-1, dtype=torch_long())
Y <- torch_tensor(match(strsplit(substr(text,2,nchar(text)),"")[[1]], chs)-1, dtype=torch_long())
embed <- nn_embedding(num_embeddings=length(chs), embedding_dim=16)
rnn <- nn_gru(input_size=16, hidden_size=64, batch_first=TRUE)
head <- nn_linear(64, length(chs))
opt <- optim_adam(c(embed$parameters, rnn$parameters, head$parameters), lr=2e-2)
for(epoch in 1:300){
  xemb <- embed(X)$unsqueeze(1)$transpose(1,2) # (1,T,16)
  out <- rnn(xemb)
  logits <- head(out[[1]]$squeeze(1))
  loss <- nnf_cross_entropy(logits, Y)
  opt$zero_grad(); loss$backward(); opt$step()
}
loss$item()
```

## Julia (Flux) variant
```{julia}
using Flux, Random
text = "In mathematics we write x^2 + y^2 = r^2. Proofs rely on axioms and logic.
" *
       "Sequences, limits, and derivatives shape analysis. Probability models uncertainty;
" *
       "linear algebra powers neural networks via matrix multiplication."
chs = sort(collect(Set(text)))
stoi = Dict(c=>i for (i,c) in enumerate(chs))
itos = Dict(i=>c for (c,i) in stoi)
X = collect(first.(Iterators.partition(map(c->stoi[c],text[1:end-1]),1)))
Y = collect(first.(Iterators.partition(map(c->stoi[c],text[2:end]),1)))
embed = Flux.Embedding(length(chs), 16)
rnn = Flux.GRU(16,64)
head = Dense(64, length(chs))
ps = Flux.params(embed,rnn,head)
loss() = begin
  xemb = embed(X)
  h = Flux.hidden(rnn)
  ys = Any[]
  for t in 1:length(X)
    h = rnn(xemb[:,t], h)
    push!(ys, head(h))
  end
  Flux.logitcrossentropy(hcat(ys...), Flux.onehotbatch(Y, 1:length(chs)))
end
opt = ADAM(2e-2)
for epoch in 1:300
  Flux.train!(x->loss(), ps, [], opt)
end
"done"
```

---

# Day 2 — Session 4: Sampling, embeddings, extensions

## Temperature & top‑k sampling (Python helper)
```{python}
import torch
def sample_with_temperature(logits, temp=1.0, top_k=None):
    l = logits / temp
    if top_k is not None:
        v, ix = torch.topk(l, top_k)
        mask = torch.full_like(l, float('-inf'))
        mask[ix] = v
        l = mask
    p = torch.softmax(l, dim=0)
    return torch.multinomial(p, 1).item()
```

## Simple TF‑IDF word embeddings + cosine

### R
```{r}
library(tidyverse)
text <- c("math loves matrices", "neural nets love matrix calculus", "probability and linear algebra")
toks <- strsplit(text, " ")
terms <- sort(unique(unlist(toks)))
D <- sapply(toks, function(doc) table(factor(terms, levels=terms)) * 0 + table(factor(doc, levels=terms)))
idf <- log(length(text) / (rowSums(D>0)+1))
tfidf <- sweep(D,1,idf,"*")
cosine <- function(a,b) sum(a*b)/sqrt(sum(a*a)*sum(b*b))
cosine(tfidf[,1], tfidf[,2])
```

### Python
```{python}
import numpy as np
text = ["math loves matrices", "neural nets love matrix calculus", "probability and linear algebra"]
terms = sorted({w for doc in text for w in doc.split()})
D = np.array([[doc.split().count(t) for doc in text] for t in terms], dtype=float)
idf = np.log(len(text) / (np.count_nonzero(D,axis=1)+1))
tfidf = (D.T * idf).T
cos = lambda a,b: (a@b)/np.sqrt((a@a)*(b@b))
cos(tfidf[:,0], tfidf[:,1])
```

### Julia
```{julia}
using LinearAlgebra
text = ["math loves matrices", "neural nets love matrix calculus", "probability and linear algebra"]
terms = sort(collect(Set(vcat([split(d) for d in text]...))))
D = [count(==(t), split(doc)) for t in terms, doc in text]
idf = log.(length(text) ./ (sum(D .> 0, dims=2) .+ 1))
tfidf = D .* idf
cos(a,b) = (a' * b) / sqrt((a' * a) * (b' * b))
cos(tfidf[:,1], tfidf[:,2])
```

---

## Assessment & Exercises
- Exit ticket: define token vs embedding; explain the benefit of a validation split.
- Mini‑project: tune hidden size/learning rate on the spiral MLP and plot decision boundaries and accuracy.
- Try dropout/L2 regularization; compare to baseline.

## Troubleshooting
- On CPU‑only laptops, keep hidden sizes small (8–32) and epochs ≤ 500–1000.
- If the GRU loss explodes, reduce the learning rate from 2e‑2 → 5e‑3.

## Next steps
- Replace GRU with a single‑head self‑attention layer on characters.
- Swap the spiral for `iris` and compare linear vs non‑linear decision boundaries.
- Explore wordpiece tokenization and subword frequency effects (conceptual demo).
