---
title: "Classification Methods: Logistic Regression, LDA & QDA"
author: "Mansour Abdoli"
ai.disclaimer: "The content is initially generated by Claude Sonnet 4"
date: "2025-09-22; last updated: `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    mathjax: "https://mathjax.rstudio.com/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(knitr)
library(kableExtra)
```

# Introduction to Classification

When the response variable is categorical, prediction is called **classification** and prediction techniques are called **classifiers**.

Common classification techniques include:

- Logistic regression
- Linear discriminant analysis (LDA)
- Quadratic discriminant analysis (QDA)
- K-nearest neighbors (KNN)

Other computer-intensive methods include:

- Generalized additive models
- Decision trees
- Random forest
- Boosting
- Support vector machines

# Logistic Regression

## Two-Level Response

Assume that a response $Y$ takes two levels (classes). Using 0/1 coding to represent those levels, we might initially consider treating the response as a numerical variable.

Using a linear regression model:
$$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \ldots + \beta_p X_p + \epsilon$$

The estimated model would be:
$$\hat{Y} = \hat{\beta}_0 + \hat{\beta}_1 X_1 + \hat{\beta}_2 X_2 + \ldots + \hat{\beta}_p X_p$$

We could classify as $\hat{Y} = 1$ if $\hat{Y} > 0.5$ and $\hat{Y} = 0$ otherwise.

**Problem**: This approximation technically models $E[Y|X]$, however, it can get values below 0 and above 1, making it hard to interpret as a probability.

**Better approach**: Model $P(Y = 1|X)$ directly, where $P(Y = 1|X)$ takes values between 0 and 1.

## The Logistic Function

In logistic regression, the probability of success is related to a linear combination of predictors through a **logistic function** to ensure that the output is always between 0 and 1:

$$P(Y = 1|X) = \frac{e^{\beta_0 + \beta_1 X_1 + \ldots + \beta_p X_p}}{1 + e^{\beta_0 + \beta_1 X_1 + \ldots + \beta_p X_p}}$$

This can be written more compactly as:
$$P(Y = 1|X) = \frac{e^{X\beta}}{1 + e^{X\beta}}$$

where $X\beta = \beta_0 + \beta_1 X_1 + \ldots + \beta_p X_p$.

It can be seen that as $X\beta$ moves from $-\infty$ to $+\infty$, $P(Y = 1|X)$ goes from 0 to 1, passing through 0.5 when $X\beta = 0$.

## The Logit Transformation

The **log-odds** (logit) of the probability of success is modeled using linear regression:

$$\text{logit}(P(Y = 1|X)) = \log\left(\frac{P(Y = 1|X)}{1 - P(Y = 1|X)}\right) = X\beta$$

This transformation linearizes the relationship between the predictors and the log-odds.

When the model is fit, we can make inferences about the parameters $\beta$ and the log-odds of probability of success, which can be transformed into inferences about the probability of success $P(Y = 1|X)$.

## Maximum Likelihood Estimation

Given $n$ observations $(x_i, y_i)$, the maximum likelihood estimate of $\beta$ is found as follows:

**Likelihood Function**: For independent Bernoulli observations:
$$L(\beta) = \prod_{i=1}^n P(Y = y_i|X = x_i)$$

Since $P(Y = y_i|X = x_i) = p_i^{y_i}(1-p_i)^{1-y_i}$ where $p_i = P(Y = 1|X = x_i)$:

$$L(\beta) = \prod_{i=1}^n p_i^{y_i}(1-p_i)^{1-y_i}$$

**Log-Likelihood**: 
$$\ell(\beta) = \sum_{i=1}^n [y_i \log(p_i) + (1-y_i) \log(1-p_i)]$$

Substituting $p_i = \frac{e^{x_i^T\beta}}{1 + e^{x_i^T\beta}}$:

$$\ell(\beta) = \sum_{i=1}^n [y_i x_i^T\beta - \log(1 + e^{x_i^T\beta})]$$

**Maximum Likelihood Estimates**: Found by setting the derivative equal to zero:
$$\frac{\partial \ell(\beta)}{\partial \beta} = \sum_{i=1}^n [y_i x_i - \frac{e^{x_i^T\beta}}{1 + e^{x_i^T\beta}} x_i] = 0$$

There is no closed-form solution for this system of equations.

## Newton-Raphson Algorithm

The maximum likelihood equation is usually solved using the **Newton-Raphson method**.

For solving $g(\beta) = 0$:
$$\beta^{(t+1)} = \beta^{(t)} - \frac{g(\beta^{(t)})}{g'(\beta^{(t)})}$$

**Score Function** (first derivative):
$$U(\beta) = \sum_{i=1}^n (y_i - p_i) x_i = X^T(y - p)$$

**Hessian Matrix** (second derivative):
$$H(\beta) = -\sum_{i=1}^n p_i(1 - p_i) x_i x_i^T = -X^T W X$$

where $W$ is a diagonal matrix with $W_{ii} = p_i(1 - p_i)$.

**Newton-Raphson Update**:
$$\beta^{(t+1)} = \beta^{(t)} + (X^T W X)^{-1} X^T (y - p)$$

## Fisher Scoring

In Fisher scoring, the Hessian $H(\beta)$ is replaced by its expectation $E[H(\beta)]$.

Note that:
$$E[y_i - p_i] = 0$$
$$\text{Var}(y_i - p_i) = p_i(1 - p_i)$$

This means the Fisher information matrix equals the negative Hessian:
$$I(\beta) = E[-H(\beta)] = X^T W X$$

The Fisher scoring update is identical to Newton-Raphson for logistic regression.

## Binomial Logistic Regression

When we have $n_i$ trials for each unique set of predictors $x_i$, with $y_i$ successes, we use the binomial distribution:

$$Y_i \sim \text{Binomial}(n_i, p_i)$$

The likelihood becomes:
$$L(\beta) = \prod_{i=1}^k \binom{n_i}{y_i} p_i^{y_i} (1-p_i)^{n_i-y_i}$$

The same estimation approach can be used with appropriate modifications.

# Generalized Linear Models

## Exponential Family

Binomial and Bernoulli distributions are members of the **exponential family** of distributions, which have the form:

$$f(y|\theta) = \exp\left(\frac{y\theta - b(\theta)}{a(\phi)} + c(y, \phi)\right)$$

where:

- $\theta$ is the natural parameter
- $\phi$ is the dispersion parameter
- $b(\cdot)$, $a(\cdot)$, and $c(\cdot)$ are known functions

**Examples**:

**Binomial**: $f(y|n,p) = \binom{n}{y} p^y (1-p)^{n-y}$

- Natural parameter: $\theta = \log\left(\frac{p}{1-p}\right)$ (logit)
- $b(\theta) = n\log(1 + e^\theta)$

**Poisson**: $f(y|\lambda) = \frac{e^{-\lambda}\lambda^y}{y!}$  

- Natural parameter: $\theta = \log(\lambda)$
- $b(\theta) = e^\theta$

**Normal**: $f(y|\mu,\sigma^2) = \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{(y-\mu)^2}{2\sigma^2}\right)$

- Natural parameter: $\theta = \mu$ 
- $b(\theta) = \frac{\theta^2}{2}$

## Link Functions

In GLMs, the natural parameter $\theta$ is modeled using a linear combination of predictors:
$$g(\mu) = X\beta$$

where $g(\cdot)$ is the **link function**.

**Common Link Functions**:

- **Normal**: Identity link $g(\mu) = \mu$ (ordinary linear regression)
- **Binomial**: Logit link $g(p) = \log\left(\frac{p}{1-p}\right)$ (logistic regression)
- **Poisson**: Log link $g(\lambda) = \log(\lambda)$ (log-linear models)

# Multinomial Logistic Regression

## K-Level Response

For a response with $K$ levels $\{0, 1, \ldots, K-1\}$, we can extend binary logistic regression.

**Reference Category Approach**: Using level 0 as the baseline:

$$P(Y = k|X) = \frac{\exp(X\beta_k)}{1 + \sum_{j=1}^{K-1} \exp(X\beta_j)} \quad \text{for } k = 1, \ldots, K-1$$

$$P(Y = 0|X) = \frac{1}{1 + \sum_{j=1}^{K-1} \exp(X\beta_j)}$$

## Softmax Coding

In the **softmax** approach, all coefficients are estimated symmetrically:

$$P(Y = k|X) = \frac{\exp(X\beta_k)}{\sum_{j=0}^{K-1} \exp(X\beta_j)} \quad \text{for } k = 0, \ldots, K-1$$

This requires a constraint for identifiability, such as $\sum_{k=0}^{K-1} \beta_k = 0$.

# Linear Discriminant Analysis (LDA)

LDA is a classification method that assumes each class has a multivariate normal distribution with a common covariance matrix.

## Bayes' Theorem for Classification

For $K$ classes, Bayes' theorem gives:
$$P(Y = k|X = x) = \frac{P(X = x|Y = k) P(Y = k)}{P(X = x)} = \frac{\pi_k f_k(x)}{\sum_{j=1}^K \pi_j f_j(x)}$$

where:

- $\pi_k = P(Y = k)$ is the prior probability of class $k$
- $f_k(x) = P(X = x|Y = k)$ is the class-conditional density

## LDA Assumptions

1. Each class follows a multivariate normal distribution:
   $$f_k(x) = \frac{1}{(2\pi)^{p/2}|\Sigma|^{1/2}} \exp\left(-\frac{1}{2}(x - \mu_k)^T \Sigma^{-1} (x - \mu_k)\right)$$

2. All classes share the same covariance matrix $\Sigma$

3. Different class means $\mu_k$

## LDA Decision Rule

The **discriminant function** for class $k$ is:
$$\delta_k(x) = x^T \Sigma^{-1} \mu_k - \frac{1}{2} \mu_k^T \Sigma^{-1} \mu_k + \log(\pi_k)$$

**Classification Rule**: Assign $x$ to class $k$ if $\delta_k(x) > \delta_j(x)$ for all $j \neq k$.

## Parameter Estimation

From training data $\{(x_i, y_i)\}_{i=1}^n$:

**Prior probabilities**: $\hat{\pi}_k = \frac{n_k}{n}$ where $n_k$ is the number of observations in class $k$

**Class means**: $\hat{\mu}_k = \frac{1}{n_k} \sum_{y_i = k} x_i$

**Common covariance matrix**: 
$$\hat{\Sigma} = \frac{1}{n-K} \sum_{k=1}^K \sum_{y_i = k} (x_i - \hat{\mu}_k)(x_i - \hat{\mu}_k)^T$$

# Quadratic Discriminant Analysis (QDA)

QDA relaxes the assumption of equal covariance matrices across classes.

## QDA Assumptions

1. Each class follows a multivariate normal distribution
2. Each class has its own covariance matrix $\Sigma_k$
3. Different class means $\mu_k$

## QDA Decision Rule

The discriminant function for class $k$ becomes:
$$\delta_k(x) = -\frac{1}{2}(x - \mu_k)^T \Sigma_k^{-1} (x - \mu_k) - \frac{1}{2}\log|\Sigma_k| + \log(\pi_k)$$

This leads to **quadratic decision boundaries** (hence the name).

## Parameter Estimation

**Class-specific covariance matrices**:
$$\hat{\Sigma}_k = \frac{1}{n_k - 1} \sum_{y_i = k} (x_i - \hat{\mu}_k)(x_i - \hat{\mu}_k)^T$$

Other parameters are estimated as in LDA.

# Comparison of Methods

```{r comparison-table, echo=FALSE}
comparison_df <- data.frame(
  Method = c("Logistic Regression", "LDA", "QDA"),
  "Decision Boundary" = c("Linear", "Linear", "Quadratic"),
  "Distributional Assumptions" = c("None", "Multivariate Normal", "Multivariate Normal"),
  "Covariance Structure" = c("Not applicable", "Common Σ", "Class-specific Σₖ"),
  "Parameters" = c("β coefficients", "μₖ, Σ, πₖ", "μₖ, Σₖ, πₖ"),
  "Flexibility" = c("Medium", "Low", "High")
)

kable(comparison_df, escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, width = "15%") %>%
  column_spec(2, width = "15%") %>%
  column_spec(3, width = "20%") %>%
  column_spec(4, width = "20%") %>%
  column_spec(5, width = "15%") %>%
  column_spec(6, width = "15%")
```

## When to Use Each Method

- **Logistic Regression**: When you don't want to assume normality; provides interpretable coefficients; works well with mixed predictor types
- **LDA**: When classes are approximately normal with similar covariance; computationally efficient; good for small sample sizes
- **QDA**: When classes have different covariance structures; more flexible than LDA but requires larger sample sizes

# Model Selection and Evaluation

## Cross-Validation
Use techniques like k-fold cross-validation to compare model performance.

## Performance Metrics

- Accuracy, Precision, Recall, F1-Score
- ROC-AUC for probability-based methods
- Confusion matrices for detailed error analysis

## Bias-Variance Tradeoff

- LDA: Lower variance, higher bias
- QDA: Higher variance, lower bias  
- Logistic Regression: Intermediate


