---
title: "Performance Measures for Classification Methods"
author: "Mansour Abdoli, PhD"
ai.disclaimer: "The content is initially generated by Claude Sonnet 4"
date: "2025-09-22; last updated: `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(knitr)
library(kableExtra)
```

# Introduction

Classification is a fundamental task in statistics and machine learning where we predict categorical outcomes. Evaluating the performance of classification models requires various metrics that capture different aspects of model quality. This document provides comprehensive definitions and formulas for the most important classification performance measures.

# Confusion Matrix

The foundation of most classification metrics is the **confusion matrix**, a table that describes the performance of a classification model:

```{r confusion-matrix, echo=FALSE}
confusion_df <- data.frame(
  " " = c("**Predicted**", "Positive", "Negative"),
  "Positive" = c("**Actual**", "TP (True Positive)", "FN (False Negative)"),
  "Negative" = c(" ", "FP (False Positive)", "TN (True Negative)")
)

kable(confusion_df, col.names = c("", "Positive", "Negative"), escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Where:

- **TP (True Positive)**: Correctly predicted positive cases
- **TN (True Negative)**: Correctly predicted negative cases  
- **FP (False Positive)**: Incorrectly predicted positive cases (Type I error)
- **FN (False Negative)**: Incorrectly predicted negative cases (Type II error)

# Basic Performance Measures

## Accuracy

**Definition**: The proportion of correct predictions out of all predictions.

$$\text{Accuracy} = \frac{TP + TN}{TP + TN + FP + FN}$$

**Range**: [0, 1], where 1 indicates perfect classification.

**When to use**: Balanced datasets where all classes are equally important.

**Limitations**: Can be misleading with imbalanced datasets.

## Precision (Positive Predictive Value)

**Definition**: The proportion of true positive predictions among all positive predictions.

$$\text{Precision} = \frac{TP}{TP + FP}$$

**Range**: [0, 1], where 1 indicates no false positives.

**Interpretation**: "Of all instances predicted as positive, how many were actually positive?"

**When to use**: When the cost of false positives is high (e.g., spam detection).

## Recall (Sensitivity, True Positive Rate)

**Definition**: The proportion of actual positive instances that were correctly identified.

$$\text{Recall} = \frac{TP}{TP + FN}$$

**Range**: [0, 1], where 1 indicates no false negatives.

**Interpretation**: "Of all actual positive instances, how many did we correctly identify?"

**When to use**: When the cost of false negatives is high (e.g., medical diagnosis).

## Specificity (True Negative Rate)

**Definition**: The proportion of actual negative instances that were correctly identified.

$$\text{Specificity} = \frac{TN}{TN + FP}$$

**Range**: [0, 1], where 1 indicates no false positives among negatives.

**Interpretation**: "Of all actual negative instances, how many did we correctly identify?"

## F1-Score

**Definition**: The harmonic mean of precision and recall.

$$\text{F1-Score} = 2 \times \frac{\text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}} = \frac{2TP}{2TP + FP + FN}$$

**Range**: [0, 1], where 1 indicates perfect precision and recall.

**When to use**: When you need a single metric that balances precision and recall.

## F-Beta Score

**Definition**: A generalization of the F1-score that allows weighting precision and recall differently.

$$\text{F}_\beta = (1 + \beta^2) \times \frac{\text{Precision} \times \text{Recall}}{\beta^2 \times \text{Precision} + \text{Recall}}$$

Where:

- $\beta > 1$: Emphasizes recall over precision
- $\beta < 1$: Emphasizes precision over recall
- $\beta = 1$: Equal weight (F1-score)

# Error Rates

## False Positive Rate (Type I Error Rate)

$$\text{FPR} = \frac{FP}{TN + FP} = 1 - \text{Specificity}$$

## False Negative Rate (Type II Error Rate)

$$\text{FNR} = \frac{FN}{TP + FN} = 1 - \text{Recall}$$

## False Discovery Rate

$$\text{FDR} = \frac{FP}{TP + FP} = 1 - \text{Precision}$$

# Probabilistic Measures

## Log-Loss (Cross-Entropy Loss)

**Definition**: Measures the performance of classification models that output probabilities.

For binary classification:
$$\text{Log-Loss} = -\frac{1}{N} \sum_{i=1}^{N} [y_i \log(p_i) + (1-y_i) \log(1-p_i)]$$

For multi-class classification:
$$\text{Log-Loss} = -\frac{1}{N} \sum_{i=1}^{N} \sum_{j=1}^{M} y_{ij} \log(p_{ij})$$

Where:

- $N$ = number of samples
- $M$ = number of classes
- $y_{ij}$ = 1 if sample $i$ belongs to class $j$, 0 otherwise
- $p_{ij}$ = predicted probability of sample $i$ belonging to class $j$

**Range**: [0, ∞), where 0 indicates perfect predictions.

## Brier Score

**Definition**: Measures the accuracy of probabilistic predictions for binary classification.

$$\text{Brier Score} = \frac{1}{N} \sum_{i=1}^{N} (p_i - y_i)^2$$

Where:

- $p_i$ = predicted probability of positive class for sample $i$
- $y_i$ = actual binary outcome (0 or 1) for sample $i$

**Range**: [0, 1], where 0 indicates perfect predictions.

# Rank-Based Measures

## ROC-AUC (Receiver Operating Characteristic - Area Under Curve)

**Definition**: Measures the model's ability to distinguish between classes across all classification thresholds.

The ROC curve plots:

- **X-axis**: False Positive Rate (FPR)
- **Y-axis**: True Positive Rate (TPR = Recall)

$$\text{AUC} = \int_0^1 \text{TPR}(\text{FPR}^{-1}(x)) dx$$

**Range**: [0, 1], where:

- 0.5 = Random classifier
- 1.0 = Perfect classifier
- 0.0 = Perfectly wrong classifier

## Precision-Recall AUC

**Definition**: The area under the precision-recall curve.

**When to use**: Particularly useful for imbalanced datasets where the positive class is rare.

# Advanced Measures

## Matthews Correlation Coefficient (MCC)

**Definition**: A balanced measure that accounts for all four confusion matrix categories.

$$\text{MCC} = \frac{TP \times TN - FP \times FN}{\sqrt{(TP + FP)(TP + FN)(TN + FP)(TN + FN)}}$$

**Range**: [-1, 1], where:

- 1 = Perfect prediction
- 0 = Random prediction
- -1 = Total disagreement

**Advantages**: Works well with imbalanced datasets and is generally regarded as a balanced measure.

## Cohen's Kappa

**Definition**: Measures inter-rater agreement, accounting for agreement that could occur by chance.

$$\kappa = \frac{p_o - p_e}{1 - p_e}$$

Where:

- $p_o$ = observed agreement (accuracy)
- $p_e$ = expected agreement by chance

For binary classification:
$$p_e = \frac{(TP + FN)(TP + FP) + (TN + FP)(TN + FN)}{(TP + TN + FP + FN)^2}$$

**Range**: [-1, 1], with interpretation similar to MCC.

## Balanced Accuracy

**Definition**: The average of recall obtained on each class.

For binary classification:
$$\text{Balanced Accuracy} = \frac{\text{Sensitivity} + \text{Specificity}}{2}$$

For multi-class:
$$\text{Balanced Accuracy} = \frac{1}{C} \sum_{i=1}^{C} \text{Recall}_i$$

Where $C$ is the number of classes.

**When to use**: Imbalanced datasets where you want equal weight for each class.

# Multi-Class Extensions

## Macro-Averaged Metrics

**Definition**: Calculate metrics for each class independently, then take the average.

$$\text{Macro-Average} = \frac{1}{C} \sum_{i=1}^{C} \text{Metric}_i$$

**Characteristics**: Gives equal weight to each class, regardless of class frequency.

## Micro-Averaged Metrics

**Definition**: Calculate metrics globally by counting total TP, FN, and FP across all classes.

For precision:
$$\text{Micro-Precision} = \frac{\sum_{i=1}^{C} TP_i}{\sum_{i=1}^{C} (TP_i + FP_i)}$$

**Characteristics**: Gives equal weight to each sample, so frequent classes have more influence.

## Weighted Average

**Definition**: Calculate metrics for each class and average them, weighted by the number of true instances for each class.

$$\text{Weighted Average} = \frac{\sum_{i=1}^{C} w_i \times \text{Metric}_i}{\sum_{i=1}^{C} w_i}$$

Where $w_i$ is typically the number of true instances of class $i$.

# Choosing the Right Metric

```{r metric-selection, echo=FALSE}
selection_df <- data.frame(
  Scenario = c(
    "Balanced dataset, all errors equally important",
    "Imbalanced dataset",
    "False positives are costly",
    "False negatives are costly", 
    "Need single balanced metric",
    "Probabilistic predictions",
    "Ranking quality important",
    "Multi-class with class imbalance"
  ),
  "Recommended Metrics" = c(
    "Accuracy",
    "Precision, Recall, F1-Score, MCC",
    "Precision, Specificity",
    "Recall, Sensitivity",
    "F1-Score, MCC",
    "Log-Loss, Brier Score",
    "ROC-AUC, PR-AUC",
    "Macro-averaged metrics, Balanced Accuracy"
  )
)

kable(selection_df, col.names = c("Scenario", "Recommended Metrics")) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, width = "40%") %>%
  column_spec(2, width = "60%")
```

# Example Calculation

```{r example-calc}
# Example confusion matrix values
TP <- 85
TN <- 90  
FP <- 10
FN <- 15
total <- TP + TN + FP + FN

# Calculate metrics
accuracy <- (TP + TN) / total
precision <- TP / (TP + FP)
recall <- TP / (TP + FN)
specificity <- TN / (TN + FP)
f1_score <- 2 * (precision * recall) / (precision + recall)

# Matthews Correlation Coefficient
mcc_num <- (TP * TN) - (FP * FN)
mcc_den <- sqrt((TP + FP) * (TP + FN) * (TN + FP) * (TN + FN))
mcc <- mcc_num / mcc_den

# Display results
results <- data.frame(
  Metric = c("Accuracy", "Precision", "Recall", "Specificity", "F1-Score", "MCC"),
  Value = round(c(accuracy, precision, recall, specificity, f1_score, mcc), 3)
)

kable(results) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Conclusion

The choice of performance metric depends heavily on the specific problem context, class distribution, and the relative costs of different types of errors. For most applications, it's recommended to evaluate multiple metrics to get a comprehensive understanding of model performance.

**Key takeaways**:

- Use accuracy for balanced datasets with equal error costs
- Use precision and recall for imbalanced datasets or when error costs differ
- Use F1-score for a single balanced metric
- Use MCC for a robust measure that works well across different scenarios
- Use ROC-AUC for comparing models across different thresholds
- Consider the business/scientific context when selecting metrics

---
