---
title: "Dimensionality Reduction & Association Rule Mining"
author: "Statistical Learning - ISLR Chapters 6.3-6.4 & 12"
format: 
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
execute:
  warning: false
  message: false
---

# Part I: Dimensionality Reduction (ISLR 6.3-6.4)

## Overview

Dimensionality reduction transforms high-dimensional data ($p$ predictors) into a lower-dimensional representation ($M < p$ features) while preserving important information. This addresses the **curse of dimensionality** and can improve model performance.

## 6.3 Principal Components Regression (PCR)

### Mathematical Foundation

**Principal Components Analysis (PCA)** finds linear combinations of predictors that capture maximum variance:

**First Principal Component:**
$$Z_1 = \phi_{11}X_1 + \phi_{21}X_2 + \cdots + \phi_{p1}X_p$$

where $\phi_1 = (\phi_{11}, \phi_{21}, \ldots, \phi_{p1})^T$ is the loading vector that maximizes $\text{Var}(Z_1)$ subject to $\sum_{j=1}^p \phi_{j1}^2 = 1$.

**Optimization Problem:**

$$\max_{\phi_{11}, \ldots, \phi_{p1}} \left\{ \frac{1}{n} \sum_{i=1}^n \left( \sum_{j=1}^p \phi_{j1} x_{ij} \right)^2 \right\} \text{ subject to } \sum_{j=1}^p \phi_{j1}^2 = 1$$

**Subsequent Components:**

- $Z_2, Z_3, \ldots, Z_p$ are orthogonal to all previous components
- Each maximizes variance among all linear combinations orthogonal to previous PCs
- Together, they form an orthogonal basis

**Key Properties:**

- PCs are ordered by variance explained: $\text{Var}(Z_1) \geq \text{Var}(Z_2) \geq \cdots \geq \text{Var}(Z_p)$
- Total variance: $\sum_{j=1}^p \text{Var}(Z_j) = \sum_{j=1}^p \text{Var}(X_j)$
- PCs are uncorrelated: $\text{Cor}(Z_i, Z_j) = 0$ for $i \neq j$

### Principal Components Regression

PCR performs regression on the first $M$ principal components:

$$y_i = \theta_0 + \theta_1 z_{i1} + \theta_2 z_{i2} + \cdots + \theta_M z_{iM} + \epsilon_i$$

where $M < p$ is chosen via cross-validation.

**Intuition:** If the response is related to the directions of high variance in $X$, PCR can outperform least squares.

### Assumptions

1. **Linearity:** Response is linear in the PCs (transformed predictors)
2. **Variance equals importance:** Directions of high variance are assumed to be associated with the response
3. **Standardization matters:** Variables should be standardized if on different scales
4. **Orthogonality:** PCs are uncorrelated by construction

### Applications

- **High-dimensional regression:** $p$ close to or exceeds $n$
- **Multicollinearity:** When predictors are highly correlated
- **Data visualization:** Project to 2D or 3D for plotting
- **Feature engineering:** Create uncorrelated features
- **Genomics:** Gene expression data ($p >> n$)
- **Image compression:** Reduce dimensionality of image data

### Things to Watch For

⚠️ **Direction of maximum variance ≠ direction of maximum association with $Y$**

   - PCR may discard useful information in low-variance directions
   - Supervised methods (PLS) may perform better

⚠️ **Standardization required**

   - If predictors have different scales, PCA is dominated by high-variance variables
   - Always standardize unless variables are naturally comparable

⚠️ **Number of components $M$**

   - Use cross-validation to select $M$
   - Too few: underfitting; too many: overfitting
   - No dimension reduction if $M = p$

⚠️ **Interpretability**

   - PCs are linear combinations of all original predictors
   - Difficult to interpret loadings
   - Not sparse (all predictors have non-zero weights)

⚠️ **Unsupervised method**

   - PCA doesn't use response variable $Y$
   - May not find components relevant to prediction

### R Implementation

```{r}
library(tidyverse)
library(pls)
library(ISLR2)

# Load data
data(Hitters)
Hitters <- na.omit(Hitters)

# Prepare data
x <- model.matrix(Salary ~ ., Hitters)[, -1]
y <- Hitters$Salary

# Standardize predictors
x_scaled <- scale(x)

# Perform PCA
pca_result <- prcomp(x_scaled, scale = FALSE) # Already scaled

# Variance explained
variance_explained <- pca_result$sdev^2 / sum(pca_result$sdev^2)

# Scree plot
data.frame(
  PC = 1:length(variance_explained),
  Variance = variance_explained,
  Cumulative = cumsum(variance_explained)
) %>%
  ggplot(aes(x = PC, y = Variance)) +
  geom_line() +
  geom_point() +
  geom_line(aes(y = Cumulative), linetype = "dashed", color = "blue") +
  labs(title = "Scree Plot", 
       y = "Proportion of Variance Explained",
       subtitle = "Solid: Individual | Dashed: Cumulative") +
  theme_minimal()

# Biplot - first two PCs
biplot(pca_result, scale = 0, cex = 0.6)

# PCR with cross-validation
set.seed(123)
pcr_fit <- pcr(Salary ~ ., data = Hitters, scale = TRUE, validation = "CV")

# CV error plot
validationplot(pcr_fit, val.type = "MSEP")

# Optimal number of components
cv_errors <- RMSEP(pcr_fit)$val[1, , ]
optimal_M <- which.min(cv_errors) - 1
cat("Optimal number of components:", optimal_M, "\n")

# Summary of PCR
summary(pcr_fit)
```

## 6.4 Partial Least Squares (PLS)

### Mathematical Foundation

PLS is a **supervised** dimensionality reduction method. It finds directions that maximize correlation with the response:

**First PLS Direction:**
$$Z_1 = \sum_{j=1}^p \phi_{j1} X_j$$

where $\phi_1$ is chosen to maximize $\text{Cor}^2(Y, Z_1)$ subject to $\sum_{j=1}^p \phi_{j1}^2 = 1$.

**Algorithm:**

1. Standardize predictors
2. Set $\hat{Y}^{(0)} = \bar{y}$
3. For $m = 1, 2, \ldots, M$:
   - Compute $\phi_{jm} = \langle X_j, Y \rangle$ (univariate regression coefficient)
   - Normalize: $\phi_m = \phi_m / \|\phi_m\|$
   - Compute $Z_m = \sum_{j=1}^p \phi_{jm} X_j$
   - Regress $Y$ on $Z_m$: $\hat{Y}^{(m)} = \hat{Y}^{(m-1)} + \hat{\theta}_m Z_m$
   - Orthogonalize each $X_j$ with respect to $Z_m$

**Key Difference from PCR:**

- PLS uses response $Y$ to guide direction selection
- First PLS component puts highest weight on variables most correlated with $Y$
- Subsequent components balance variance and correlation with $Y$

### Assumptions

1. **Linearity:** Response is linear in PLS components
2. **Correlation matters:** Assumes response is related to high-correlation directions
3. **Standardization:** Variables should be standardized
4. **Sequential construction:** Each component uses residualized predictors

### Applications

Same as PCR, but particularly useful when:

- Response-predictor relationship exists in low-variance directions
- Prediction is more important than interpretation
- **Chemometrics:** Spectroscopy data (original application)
- **Quantitative structure-activity relationships (QSAR)**

### PCR vs PLS Comparison

| Aspect | PCR | PLS |
|--------|-----|-----|
| Supervision | Unsupervised | Supervised |
| Objective | Maximize variance | Maximize correlation with $Y$ |
| When better | Response relates to high-variance directions | Response relates to high-correlation directions |
| Interpretation | Slightly easier (variance-based) | Slightly harder |
| Computational | Faster | Slightly slower |

### Things to Watch For

⚠️ **Similar issues to PCR:**

   - Still requires cross-validation for $M$
   - Still not sparse (uses all predictors)
   - Still requires standardization

⚠️ **Not always better than PCR**

   - If $Y$ is related to high-variance directions, PCR may be sufficient
   - PLS can overfit if $M$ too large

⚠️ **Interpretation**

   - Even harder to interpret than PCR
   - Components are response-dependent

⚠️ **Overfitting risk**

   - By focusing on correlation with $Y$, PLS can overfit more easily
   - Critical to use proper cross-validation

### R Implementation

```{r}
# PLS with cross-validation
set.seed(123)
pls_fit <- plsr(Salary ~ ., data = Hitters, scale = TRUE, validation = "CV")

# CV error plot
validationplot(pls_fit, val.type = "MSEP")

# Optimal number of components
pls_cv_errors <- RMSEP(pls_fit)$val[1, , ]
optimal_M_pls <- which.min(pls_cv_errors) - 1
cat("Optimal number of components (PLS):", optimal_M_pls, "\n")

# Compare PCR vs PLS
comparison_df <- data.frame(
  Components = 0:(length(cv_errors) - 1),
  PCR = cv_errors,
  PLS = pls_cv_errors
) %>%
  pivot_longer(cols = c(PCR, PLS), names_to = "Method", values_to = "RMSEP")

ggplot(comparison_df, aes(x = Components, y = RMSEP, color = Method)) +
  geom_line(linewidth = 1) +
  geom_point() +
  labs(title = "PCR vs PLS Cross-Validation Error",
       y = "Root Mean Squared Error of Prediction") +
  theme_minimal()

# Summary
summary(pls_fit)
```

---

# Part II: Association Rule Mining (ISLR Chapter 12)

## Overview

Association rule mining discovers interesting relationships (associations) between variables in large databases. Originally developed for **market basket analysis**.

**Goal:** Find rules of the form $\{A\} \Rightarrow \{B\}$ meaning "if A, then B"

## Mathematical Foundation

### Basic Concepts

**Itemset:** A collection of items, e.g., $\{milk, bread\}$

**Transaction:** A set of items purchased together

**Support:** Frequency of an itemset in the dataset

$$\text{support}(A) = \frac{\text{\# transactions containing} A}{\text{total \# transactions}}$$


**Confidence:** Conditional probability
$$\text{confidence}(A \Rightarrow B) = \frac{\text{support}(A \cup B)}{\text{support}(A)} = P(B|A)$$

**Lift:** Measure of dependence
$$\text{lift}(A \Rightarrow B) = \frac{\text{support}(A \cup B)}{\text{support}(A) \times \text{support}(B)} = \frac{P(A \cap B)}{P(A)P(B)}$$

### Interpreting Metrics

**Support:**

- High support: Frequent pattern
- Low support: Rare pattern
- Minimum threshold filters noise

**Confidence:**

- Range: [0, 1]
- Confidence = 1: Perfect implication ($A$ always leads to $B$)
- Confidence = support$(B)$: Independence (rule is useless)

**Lift:**

- Lift > 1: Positive association ($A$ and $B$ occur together more than expected)
- Lift = 1: Independence (no association)
- Lift < 1: Negative association ($A$ and $B$ occur together less than expected)

### Example

Database with 10,000 transactions:

- $\{milk\}$: 4,000 transactions → support = 0.40
- $\{bread\}$: 3,000 transactions → support = 0.30
- $\{milk, bread\}$: 2,000 transactions → support = 0.20

**Rule:** $\{milk\} \Rightarrow \{bread\}$

- Support = 0.20 (20% of all transactions)
- Confidence = 2000/4000 = 0.50 (50% of milk buyers also buy bread)
- Lift = 0.20 / (0.40 × 0.30) = 1.67 (milk and bread bought together 67% more than expected)

## The Apriori Algorithm

### Core Principle

**Apriori Property:** If an itemset is frequent, all its subsets must also be frequent.

**Contrapositive:** If an itemset is infrequent, all its supersets must be infrequent.

### Algorithm Steps

1. **Find frequent 1-itemsets** ($L_1$): Count support for all items
2. **Generate candidate 2-itemsets** ($C_2$): Combine frequent 1-itemsets
3. **Prune** $C_2$: Remove itemsets with infrequent subsets
4. **Count support** for remaining candidates in $C_2$
5. **Find frequent 2-itemsets** ($L_2$): Keep those above minimum support
6. **Repeat** for $k$-itemsets until no frequent itemsets found
7. **Generate rules** from frequent itemsets

### Pseudocode

```
Apriori(T, min_support):
  L_1 = {frequent 1-itemsets}
  k = 2
  
  while L_{k-1} is not empty:
    C_k = generate_candidates(L_{k-1})  # Join step
    C_k = prune(C_k, L_{k-1})           # Prune step
    
    for transaction t in T:
      for candidate c in C_k:
        if c ⊆ t:
          c.count++
    
    L_k = {c in C_k : c.support >= min_support}
    k = k + 1
  
  return ∪_k L_k
```

## Applications

### Market Basket Analysis

- **Retail:** Product placement, cross-selling
- **E-commerce:** Recommendation systems
- **Example:** "Customers who bought diapers also bought beer"

### Healthcare

- **Disease patterns:** Co-occurring symptoms or conditions
- **Treatment effectiveness:** Drug combinations
- **Example:** "Patients with diabetes often have hypertension"

### Web Usage Mining

- **Click-stream analysis:** User navigation patterns
- **Content recommendations:** Pages visited together
- **Example:** "Users who view page A often proceed to page B"

### Other Applications

- **Bioinformatics:** Gene expression patterns
- **Fraud detection:** Suspicious transaction patterns
- **Text mining:** Word associations in documents
- **Network intrusion detection:** Attack patterns

## Assumptions

1. **Binary data:** Items are present/absent (can extend to categorical)
2. **Independence of transactions:** Each transaction is independent
3. **Equal importance:** All items weighted equally (unless specified)
4. **Completeness:** Database represents the population pattern
5. **Stationarity:** Patterns don't change over time (within analysis period)

## Things to Watch For

### ⚠️ Computational Complexity

**Problem:** Number of possible itemsets grows exponentially

- $p$ items → $2^p - 1$ possible itemsets
- 20 items → ~1 million itemsets
- 100 items → ~$10^{30}$ itemsets

**Solution:**

- Set appropriate minimum support threshold
- Apriori pruning drastically reduces search space
- Use sampling for very large datasets

### ⚠️ Parameter Selection

**Minimum Support:**

- Too high: Miss rare but important patterns
- Too low: Too many rules, high computational cost
- **Guideline:** Start with 5-10%, adjust based on results

**Minimum Confidence:**

- Too high: Miss interesting but moderate associations
- Too low: Many spurious rules
- **Guideline:** 60-80% typical

**Minimum Lift:**

- Should be > 1 for interesting rules
- **Guideline:** 1.5+ indicates strong association

### ⚠️ Spurious Associations

**Multiple Testing Problem:**

- Testing thousands of rules increases false positives
- **Solution:** Use higher thresholds, statistical tests, or Bonferroni correction

**Simpson's Paradox:**

- Association may reverse when controlling for confounders
- **Solution:** Stratified analysis, domain knowledge

### ⚠️ Interpretation Challenges

**Correlation ≠ Causation:**

- High lift doesn't imply causal relationship
- Example: Ice cream sales and drowning both correlate with temperature

**Directionality:**

- $A \Rightarrow B$ doesn't imply $B \Rightarrow A$
- Confidence is asymmetric

**Temporal ordering:**

- Rules don't capture time sequence
- May need sequential pattern mining

### ⚠️ Data Quality Issues

**Missing values:**

- Affects support calculation
- May need imputation or special handling

**Rare items:**

- Long-tail distribution common
- May need separate analysis for rare items

**Data sparsity:**

- High-dimensional data often sparse
- Affects reliability of estimates

### ⚠️ Actionability

**Trivial rules:**

- $\{bread, butter\} \Rightarrow \{milk\}$ might be obvious
- **Filter:** Use domain knowledge, remove redundant rules

**Interestingness:**

- Statistical significance ≠ business value
- **Consider:** Profit, inventory, customer value

## R Implementation

```{r}
library(arules)
library(arulesViz)

# Load example data
data("Groceries")

# Inspect data
summary(Groceries)
inspect(head(Groceries, 3))

# Visualize item frequency
itemFrequencyPlot(Groceries, topN = 20, type = "absolute",
                  main = "Top 20 Most Frequent Items")

# Apply Apriori algorithm
rules <- apriori(Groceries, 
                 parameter = list(support = 0.001,    # Min 0.1% of transactions
                                  confidence = 0.6,   # Min 60% confidence
                                  minlen = 2))        # At least 2 items

# Summary of rules
summary(rules)

# Inspect top rules by lift
top_rules <- sort(rules, by = "lift", decreasing = TRUE)
inspect(head(top_rules, 10))

# Visualize rules
plot(rules, method = "scatterplot", measure = c("support", "confidence"),
     shading = "lift", main = "Association Rules")

# Network graph for top rules
top_20 <- head(sort(rules, by = "lift"), 20)
plot(top_20, method = "graph", main = "Top 20 Rules by Lift")

# Grouped matrix
plot(rules, method = "grouped", main = "Grouped Rules Matrix")

# Find rules with specific items
milk_rules <- subset(rules, items %in% "whole milk")
inspect(head(sort(milk_rules, by = "lift"), 5))

# Find rules: antecedent contains yogurt, consequent contains milk
specific_rules <- subset(rules, 
                         lhs %in% "yogurt" & rhs %in% "whole milk")
inspect(specific_rules)

# Rule redundancy
redundant <- is.redundant(rules)
rules_pruned <- rules[!redundant]
cat("Original rules:", length(rules), "\n")
cat("Non-redundant rules:", length(rules_pruned), "\n")
```

## Advanced Metrics

### Conviction

Measures implication strength:
$$\text{conviction}(A \Rightarrow B) = \frac{1 - \text{support}(B)}{1 - \text{confidence}(A \Rightarrow B)}$$

- Conviction = 1: Independence
- Conviction = ∞: Perfect implication
- Higher values indicate stronger rules

### Cosine Similarity

$$\text{cosine}(A, B) = \frac{\text{support}(A \cup B)}{\sqrt{\text{support}(A) \times \text{support}(B)}}$$

### Kulczynski Measure

$$\text{Kulc}(A, B) = \frac{1}{2}\left[\frac{\text{support}(A \cup B)}{\text{support}(A)} + \frac{\text{support}(A \cup B)}{\text{support}(B)}\right]$$

```{r}
# Calculate additional metrics
quality(rules) <- cbind(quality(rules), 
                        conviction = interestMeasure(rules, "conviction", 
                                                     transactions = Groceries),
                        cosine = interestMeasure(rules, "cosine", 
                                                transactions = Groceries))

# Inspect rules with new metrics
inspect(head(sort(rules, by = "conviction"), 5))
```

## Best Practices

### 1. Exploratory Analysis

- Examine item frequency distribution
- Identify rare vs common items
- Check for data quality issues

### 2. Iterative Tuning

- Start with higher thresholds
- Gradually lower to find sweet spot
- Balance number of rules vs interestingness

### 3. Domain Knowledge

- Filter rules using business logic
- Focus on actionable insights
- Consult domain experts

### 4. Validation

- Use holdout set for validation
- Test rules on new data
- Monitor rule stability over time

### 5. Post-Processing

- Remove redundant rules
- Rank by multiple metrics
- Visualize for insights

## Summary Comparison

| Method | Type | Supervision | Output | Best For |
|--------|------|-------------|--------|----------|
| PCR | Dimension Reduction | Unsupervised | Continuous predictions | High-dimensional regression |
| PLS | Dimension Reduction | Supervised | Continuous predictions | Response-guided reduction |
| Association Rules | Pattern Mining | Unsupervised | If-then rules | Discovering relationships |

## Key Takeaways

### Dimensionality Reduction

1. Use when $p$ is large or predictors are correlated
2. Always standardize predictors
3. Use cross-validation to select number of components
4. PCR for variance-based reduction, PLS for response-guided
5. Trade-off: dimension reduction vs information loss

### Association Rules

1. Requires appropriate minimum support/confidence/lift thresholds
2. Apriori algorithm efficiently prunes search space
3. Watch for spurious associations (multiple testing)
4. Focus on actionable and non-obvious rules
5. Always consider domain knowledge in interpretation

# References

- James, G., Witten, D., Hastie, T., & Tibshirani, R. (2021). *An Introduction to Statistical Learning* (2nd ed.), Chapters 6.3-6.4, 12
- Agrawal, R., & Srikant, R. (1994). "Fast Algorithms for Mining Association Rules"
- Hahsler, M., Grün, B., & Hornik, K. (2005). "arules: Mining Association Rules and Frequent Itemsets"
